Combinatorial Mixture Models for Single-Cell Assays with Application to Vaccine Studies

### 2012-07-27 MIMOSA.tex
Defined Observed False Discovery Rate and referenced Storey paper on FDR.
Signed-off-by: Greg Finak <gfinak@fhcrc.org>

\section{Results}
\label{s:results}
In this section, we apply our MIMOSA model to the data described in Section \ref{s:data}, and present the results of a simulation study based on the ICS data. The performance of MIMOSA was evaluated and compared against Fisher's exact test, the likelihood ratio test, and log fold-change by ROC (receiver operator characteristic) curve analysis and by comparing the observed FDR (false discovery rate) against the nominal FDR for each data set.

>>>>

\section{Results}
\label{s:results}
In this section, we apply our MIMOSA model to the data described in Section \ref{s:data}, and present the results of a simulation study based on the ICS data. The performance of MIMOSA was evaluated and compared against Fisher's exact test, the likelihood ratio test, and log fold-change by ROC (receiver operator characteristic) curve analysis and by comparing the \textit{observed FDR} (false discovery rate), defined as $\frac{\text{\# of false positives}}{\text{\# of observations called positive}}$ against the \textit{nominal FDR} (expected false discovery rate) for each data set~\citep{Storey:2002vj}.
